---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# poetrytools

- Performs [prosodic](https://en.wikipedia.org/wiki/Prosody_%28linguistics%29) analysis of poetry. 
- Estimates rhyme scheme and metre using CMUDict, compares them against common forms using [Levenshtein distance](https://en.wikipedia.org/wiki/Levenshtein_distance), and combines the results to guess the form of the poem. 
- Contains a `rhymes` function that is faster than any other I have found.
- Contributions & pull requests welcome.


## Installation

Requirements
------------
- Python 2.7 or Python 3
- python-Levenshtein==0.12.0

Install with ```python setup.py install```

You can install poetrytools from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MHenderson/poetrytools")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r}
library(poetrytools)
rhymes('show', 'hello')
```

```{r}
haiku <- "savannah dust trails
 whistling thorn hovers above
 hungry giraffe grows"

poem <- tokenize(haiku) # need to tokenize the poem first
scanscion(poem)
```

```{r}
guess_form(poem)
```

```{r}
limerick <- "The limerick packs laughs anatomical
 Into space that is quite economical.
 But the good ones I've seen
 So seldom are clean
And the clean ones so seldom are comical."

poem <- tokenize(limerick)
guess_form(poem, verbose = TRUE)
```

Notes
------------

- For various reasons this library currently only works for short poems; the longer the poem is, the more inaccurate it gets.
- CMUDict is included as a JSON file in order to avoid importing the behemoth that is NLTK.
